---
title: "Tuberculosis - World Distribution and Awareness" 
author: "Goh Bian Chiat, Chong Ming Keat, Tan Chee Siang, Sofia Atikah"
date: "30 May 2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::knit_hooks$set(output = function(x, options){
  if(!is.null(options$max_height)){
    paste('<pre style = "max-height:',
          options$max_height, 
          ';float: left; width: 910px; overflow-y: auto;">',
          x,
          "</pre>",
          sep = "")
  }else{
    x
  }
  
})


# import library
library(jsonlite)
library(geojsonio)
library(leaflet)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(wordcloud)
library(tm)
library(scales)
library(stringr)
library(lubridate)
library(reshape2)
library(ggcorrplot)
library(highcharter)
library(lattice)
library(treemap)
library(tidyr)

# setwd('C:/Users/bianchiat.goh/Desktop/Pvvvvv/Personal Developement/Master Study/WQD7001/WQD7001 Assignment/WQD7001 Group Assignment/R Code-final')
df<-read.csv("TB Combined dataset_3.csv",na.strings = NA,fill = NA)


df1<-df %>%
  filter(Year=="2016")%>%
  group_by(Country)


df1$Confirm_cases_RR.MDR<-as.numeric(df1$Confirm_cases_RR.MDR)
```

## Significance/Motivation
- Usually caused by *Mycobacterium tuberculosis* bacteria that generally affects the lungs.
- TB patient suffer from coughing, it also ejected the TB germ. The germ can travel airborne and only several (of the germ) can infect a healthy person nearby, hence making TB a very contagious disease. 
- Tuberculosis ranked as the 2nd leading infectious causes of deaths, and one of the most burden-inflicting disease in the world. 
- In 2017, 10 million patient fell ill, with 1.6 million patient died from the disease.
- One of the most serious concern of TB is the raise of multidrug-resistant TB (MDR-TB) and even the more severe extensive drug-resistance TB (XDR-TB) due the inappropriate and incorrect TB prescription. 


## Data Info

The data of tuberculosis were obtained from:

- [Source-Data Repository for WHO Tuberculosis](http://apps.who.int/gho/data/node.main.1315?lang=en).
- [Boston University – Rutgers University Tuberculosis Research Unit (BU-RU TBRU)](https://www.bumc.bu.edu/tbru/).
- [Mayo Clinic Tuberculosis](https://www.bumc.bu.edu/tbru/).
- [WHO Tuberculosis](https://www.who.int/news-room/fact-sheets/detail/tuberculosis).
- [Wikipedia Tuberculosis](https://en.wikipedia.org/wiki/Tuberculosis). 


## Top 5 Highest Multi Drug Resistance TB incident in 2016 by country
- Top 3 highest country in confirm cases of RR/MDR TB make up for 54% of worldwide total RR/MRD Cases.
```{r,echo=FALSE,max_height = "200px"}

TSpecial <- ttheme_minimal(
  core=list(bg_params = list(fill = blues9[1:4], col=NA),
            fg_params=list(fontface=6)),
  colhead=list(fg_params=list(col="olivedrab", fontface=4L)),
  rowhead=list(fg_params=list(col="orangered4", fontface=3L)))

df1%>%
  select(Country,Confirm_cases_RR.MDR) %>%
  arrange(desc(Confirm_cases_RR.MDR)) %>%
  head(5)%>%
  grid.table(theme = TSpecial)

```



## Global TB Heatmap

The dashboard of this presentation can be found on [Shiny App](https://bianchiat.shinyapps.io/WQD7001_Group_One_Presentation/).
<br>
<br>
The code can be found on this [Github](https://github.com/bianchiat/WQD7001) repository. 

